\sysfull

### 2017-11-12 paper/coalescing.tex
First two paragraphs of coalescing section rewritten

\sys dynamically {\em coalesces} consecutively executing tasks at run time. When two tasks are coalesced, the first of the two tasks does not commit its updates to protected memory locations when it reaches a \transition statement. Instead, execution immediately continues from the beginning of the second of the two tasks. At the end of the second of the two coalesced tasks, \sys commits the pages that were updated by either of the coalescing tasks. The purpose of coalescing is to better amortize the run time overhead of committing updated pages when a task ends. If consecutive tasks access the same pages of data, the pages accessed by both tasks only need to be committed once.

>>>>

Often, energy available at the transiently-powered device is sufficient to run multiple consecutive tasks without page commit at each task boundary. In this case task-based execution model can better amortize the run time overhead of committing updated pages when a task ends. Hence many tasks can be \emph{merged} into a single virtual task---a process we call \emph{coalescing}.

\sys, as the first task-based execution model, dynamically coalesces consecutively executing tasks at run time. When $X$ tasks are coalesced, the $X-1$ tasks do not commit their updates to protected memory locations when reaching a \transition statement. Instead, execution immediately continues from the beginning of the $X$th task. At the end of the $X$th coalesced task, \sys commits the pages that were updated by any of the $X$ coalescing tasks. If consecutive tasks access the same pages of data, the pages accessed by both tasks only need to be committed once.
